---
title: "Solutions"
author: "Ziqing Wang"
date: "2022-11-29"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(readr)
library(viridis)
library(forcats)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 2

```{r import homicide data}
homi_data = read_csv("./data/homicide-data.csv") %>% janitor::clean_names()
homi_data
```

```{r}
homi_data = homi_data %>%
  filter(victim_age != "Unknown",
         victim_race %in% c("White", "Black"),
         !victim_sex == "Unknown") %>%
  mutate(city_state = str_c(city, state, sep = ", "),
         resolved = !disposition %in% c("Closed without arrest", "Open/No arrest"),
         victim_age = as.numeric(victim_age)) %>%
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))

homi_data
```

Run a logistic regression for Baltimore, MD:

```{r}
Baltimore_fit = homi_data %>%
  filter(city_state == "Baltimore, MD") %>%
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>%
  broom::tidy(conf.int = T, conf.level=0.95) %>% 
  mutate(OR = exp(estimate),
         conf_low = exp(conf.low),
         conf_high = exp(conf.high)) %>%
  select(term, OR, conf_low, conf_high)

Baltimore_fit
```

Run the same logistic regression for each city. To do this, first write the following function:
```{r}
city_glm = function(city_state_name){
  fit = homi_data %>%
    filter(city_state == city_state_name) %>%
    glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>%
    broom::tidy(conf.int = T, conf.level=0.95) %>% 
    mutate(OR = exp(estimate),
           conf_low = exp(conf.low),
           conf_high = exp(conf.high)) %>%
    select(term, OR, conf_low, conf_high)

  return(fit)
}

```

Then use the map function:
```{r}
city_result = tibble(
  city_states = unique(homi_data$city_state),
  model_fits = map(city_states, city_glm)
) %>% unnest(model_fits) %>%
  filter(term == "victim_sexMale")

city_result 
```
Below is a plot that shows the estimated ORs and CIs for each city that compare resolved homicide cases among male vectims with female victims.
```{r}
city_result %>% 
  mutate(city_states = fct_relevel(city_states, "OR")) %>%
  ggplot(aes(y = city_states, x = OR)) +
  geom_point() +
  geom_errorbar(aes(xmin = conf_low, xmax = conf_high))
```


## Problem 3

Import the data:
```{r}
bwt_data = read_csv("./data/birthweight.csv")
bwt_data
```

Check for missing values in all variables:
```{r}
check_missing = function(col_name){
  return (tibble(
    col_name = col_name,
    n_missing = sum(is.na(bwt_data[[col_name]]))
  ))
}

map_df(names(bwt_data), check_missing)
```
There is no missing values in the data set. We proceed to data cleaning:
```{r}
bwt_data = bwt_data %>%
  mutate(babysex = fct_recode(factor(babysex), male = "1", female = "2"),
         frace = fct_recode(factor(frace), white = "1", black = "2", asian = "3", puerto_rican = "4", other = "8", unknown = "9"),
         malform = fct_recode(factor(malform), absent = "0", present = "1"),
         mrace = fct_recode(factor(mrace), white = "1", black = "2", asian = "3", puerto_rican = "4", other = "8")) 

bwt_data
```

Use stepwise regression to select a multiple linear regression model for birth weight:
```{r}

```






